---
title: "Demo"
author: "Miaolei Bao" 
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Demo}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# How to install
This package is called `SphericalKDE`. To install, run the following code (in R):

```{r, eval = FALSE}
library(devtools)
devtools::install_github("Bao-Miaolei/KDE_spherical")
```

Upon completion, you can run the following code (in R):
```{r}
library(SphericalKDE)
```

# Import data
This is a demo vignette for our package. We will use earthquake data with 77 observations contained in the ’spherepc’ package for demonstration. The data record significant earthquakes (8+ Mb magnitude) around the Pacific Ocean since 1900, collected by the U.S. Geological Survey. The data have longitude and latitude coordinates. 

```{r}
library(spherepc)

# Import earthquake data and select longitude and latitude coordinates
data(Earthquake)
earthquake <- cbind(Earthquake$long, Earthquake$lat)
head(earthquake)
```

# Data transformation

We want to transform spherical coordinates (longitude, latitude) to 3-dim Euclidean coordinates for analysis.

```{r}
earthquake_Euc <- SphericalKDE::transform_coordinates(earthquake)
head(earthquake_Euc)
```

# Cross validation

Then we could use cross validation to select the optimal smoothing parameter $\kappa$.
```{r}
kappa_list <- 10^seq(1, 3, length.out = 100)
optimal_kappa <- SphericalKDE::cv(kappa_list, earthquake_Euc)
optimal_kappa
```

# Visualization
```{r, out.width = '100%'}
library(htmlwidgets)
my_plotly_plot <- SphericalKDE::generate_plot(earthquake_Euc, kappa = optimal_kappa)
my_plotly_plot
#plotly_html <- htmlwidgets::saveWidget(my_plotly_plot, "my_plotly_plot.html")
```

